\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-03 manuscript/manuscript.tex
1/30 Notes

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}\mc{addressed}
$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
.75\}$, and
sample size $n \in \{100, 200, 400, 800}$. These distributions
were chosen to compare results on normal and non-normal
error structures, and the parameters were chosen so that the distributions
have the same mean 8 and variance 8. To generate 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is gamma. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values 
for the test when applied to samples from the same data generating process.

>>>>

We generated time series with marginal distributions $N(8, 8)$ and
\jy{why choose these two distributions?}\mc{addressed}
$\Gamma(8, 1)$, Kendall's $\tau \in \{-.75, -.5, -.25, 0, .25, .5, 
.75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. These distributions
were chosen to compare results on normal and non-normal
error structures, and the parameters were chosen so that the distributions
have the same mean 8 and variance 8. To generate 
For the purposes of 
evaluating if the test holds it size, when $X_t \sim N(8, 8)$, we tested that the 
marginal distribution family is normal, and when $X_t \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is gamma. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
For each setting for $F$, $\tau$, and $n$, we replicate the method 1000 times 
to get the distribution of the p-values 
for the test when applied to samples from the same data generating process.
